Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-19 concl.tex
up to conclusion

\section{Conclusion}
We presented a finite time performance analysis of LSAs with CS-PR and showed that the MSE decays at a rate $O(\frac{1}{t})$. Our results extended the analysis of \citet{bach} for SGD with CS-PR for the problem of linear regression with quadratic loss and \iid sampling to general LSAs with CS-PR. Our results were directly applicable to TD class of algorithms that are LSAs. In particular, new performance bounds for TDC follows from our results. Our results also improved the rates in the case of the GTD class of algorithms. We presented conditions under which a constant step-size can be chosen uniformly for a give class of data distributions. We showed a negative result in that not all data distributions `admit' such a constant step-size. This is a negative result from the perspective of TD algorithms in RL. We also argued heuristically that a constant step-size can be obtained in an automatic manner for a given LSA and a given data distribution. Thus, LSAs with CS-PR technique $i)$ achieves comparable or better error rates $ii)$ alongside automatic tuning of the constant step-size can perform comparably well in practice.

>>>>

\section{Conclusion}
We presented a finite time performance analysis of LSAs with CS-PR and showed that the MSE decays at a rate $O(\frac{1}{t})$. Our results extended the analysis of \citet{bach} for SGD with CS-PR for the problem of linear least-squares estimation and \iid sampling to general LSAs with CS-PR. Our results were directly applicable to TD class of algorithms that are LSAs. In particular, new performance bounds for TDC follows from our results. Our results also improved the rates in the case of the GTD class of algorithms. We presented conditions under which a constant step-size can be chosen uniformly for a give class of data distributions. We showed a negative result in that not all data distributions `admit' such a constant step-size. This is a negative result from the perspective of TD algorithms in RL. We also argued heuristically that a constant step-size can be obtained in an automatic manner for a given LSA and a given data distribution. Thus, LSAs with CS-PR technique $i)$ achieves comparable or better error rates $ii)$ alongside automatic tuning of the constant step-size can perform comparably well in practice.

### 2017-05-19 instance.tex
up to conclusion

%!TEX root =  flsa.tex
\section{Main Results and Discussion}\label{sec:mainresults}
In this section, we derive instance dependent bounds that are valid for a given problem $P$ (satisfying \Cref{assmp:lsa}) and in the \cref{sec:uniform}, we address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions (problems). Here, we only present the main results followed by a discussion. The detailed proofs can be found in \cref{sec:proofs}. 
\todoc{Usually it is expected that one gives an outline of the proof technique. Especially in a theory paper. At least verbally we could explain the tools used, how the proof is similar and/or different to previous proofs.}
In what follows, for the sake of brevity, we drop the subscript $P$ in the quantities $\EEP{\cdot}$, $\sigma^2_{A_P}$ and $\sigma^2_{b_P}$. \todoc{I dropped $P$ from $\EEP{\cdot}$ before. Either put there back, or remove $\EEP{\cdot}$ from here.}
%\begin{lemma}\label{lm:simtran}[Similarity Transformation]
%Let $P$ be Hurwitz, then there exists a $U\in \gln$ such that $P_U$ is positive definite.
%\end{lemma}
We start with a lemma, which is needed to meaningfully state our main result:
\begin{lemma}\label{lm:hur}
Let $P$ be a distribution over $\R^d\times \R^{\dcd}$ satisfying \Cref{assmp:lsa}. 
Then there exists an $\alpha_{P_U}>0$ and $U\in \gln$ such that $\rhod{P_U}>0$ and $\rhos{P_U}>0$
holds for all $\alpha \in (0,\alpha_{P_U})$. 
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}

@@

%\vspace*{0.5em}
%\subsection{Result Discussion}
%\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\textbf{Role of $U$}: When the given problem $P$ is positive definite, it is straightforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$ by considering the definitions of $\rhos{P}$ and $\rhod{P}$. 
However, the problem $P$ being Hurwitz does not guarantee positive definiteness (see \Cref{ex:pdas}). 
Following  \cite{lihong}, we remedy this 
by applying a similarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. This can be done because any Hurwitz matrix is similar to a PD matrix. 
Taking $U$ to be this similarity matrix, we transform  \eqref{conststep} by premultiplying it by $U^{-1}$ and introducing a new variable $\gamma_t\eqdef U^{-1 }\theta_t$.
\if0
To see how this works, let $\gamma_t\eqdef U^{-1 }\theta_t$. Premultiplying 
 \eqref{conststep} by $U^{-1}$ and plugging in $\gamma_t$, we get
\begin{align*}
%U^{-1}\theta_t&=U^{-1}\theta_{t-1}+\alpha(U^{-1} b_t- U^{-1}A_t U U^{-1}\theta_{t-1}),\\
\gamma_t&=\gamma_{t-1}+\alpha(U^{-1} b_t- J_t\gamma_{t-1}),
\end{align*}
where $J_t = U^{-1}A_t U$.
Now, since any Hurwitz matrix is similar to a PD matrix with an appropriate similarity transformation $U$, choosing $U$ this way we get that $\E[J_t]$ is PD, hence $P_U$ is PD.
\fi
%This completes the transformation of a Hurwitz problem $P$ to a positive definite problem $P_U$. 
The condition number $\cond{U}$ appears in our bound because $\theta_t$ is recovered from $\gamma_t$ using
$\theta_t=U\gamma_t$. Of course, when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. 
More generally, one can always take $U$ in the result that leads to the smallest bound.

>>>>

%!TEX root =  flsa.tex
\section{Main Results and Discussion}\label{sec:mainresults}
In this section, we derive instance dependent bounds that are valid for a given problem $P$ (satisfying \Cref{assmp:lsa}) and in the \cref{sec:uniform}, we address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions (problems). Here, we only present the main results followed by a discussion. The detailed proofs can be found in \cref{sec:proofs}. 
\todoc{Usually it is expected that one gives an outline of the proof technique. Especially in a theory paper. At least verbally we could explain the tools used, how the proof is similar and/or different to previous proofs.}
In what follows, for the sake of brevity, we drop the subscript $P$ in the quantities $\EEP{\cdot}$, $\sigma^2_{A_P}$ and $\sigma^2_{b_P}$. \todoc{I dropped $P$ from $\EEP{\cdot}$ before. Either put there back, or remove $\EEP{\cdot}$ from here.}
%\begin{lemma}\label{lm:simtran}[Similarity Transformation]
%Let $P$ be Hurwitz, then there exists a $U\in \gln$ such that $P_U$ is positive definite.
%\end{lemma}
We start with a lemma, which is needed to meaningfully state our main result:
\begin{lemma}\label{lm:hur}
Let $P$ be a distribution over $\R^d\times \R^{\dcd}$ satisfying \Cref{assmp:lsa}. \todoc{Is it important that the distribution is over real-valued stuff? Would the results work for complexed-valued data? I would think so.}
Then there exists an $\alpha_{P_U}>0$ and $U\in \gln$ such that $\rhod{P_U}>0$ and $\rhos{P_U}>0$
holds for all $\alpha \in (0,\alpha_{P_U})$. 
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}

@@

%\vspace*{0.5em}
%\subsection{Result Discussion}
%\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\textbf{Role of $U$}: When the given problem $P$ is positive definite, it is straightforward to produce an $\alpha_P>0$ such that $\rhos{P}>0$ and $\rhod{P}>0,\,\forall \alpha\in(0,\alpha_P)$ by considering the definitions of $\rhos{P}$ and $\rhod{P}$. 
However, the problem $P$ being Hurwitz does not guarantee positive definiteness. % (see \Cref{ex:pdas}). 
\todoc{I commented out the examples.}
Following  \cite{lihong}, we remedy this 
by applying a similarity transformation using an appropriate $U$ that transforms a Hurwitz problem $P$ to a positive definite problem $P_U$. This can be done because any Hurwitz matrix is similar to a PD matrix. 
Taking $U$ to be this similarity matrix, we transform  \eqref{conststep} by premultiplying it by $U^{-1}$ and introducing a new variable $\gamma_t\eqdef U^{-1 }\theta_t$.
\if0
To see how this works, let $\gamma_t\eqdef U^{-1 }\theta_t$. Premultiplying 
 \eqref{conststep} by $U^{-1}$ and plugging in $\gamma_t$, we get
\begin{align*}
%U^{-1}\theta_t&=U^{-1}\theta_{t-1}+\alpha(U^{-1} b_t- U^{-1}A_t U U^{-1}\theta_{t-1}),\\
\gamma_t&=\gamma_{t-1}+\alpha(U^{-1} b_t- J_t\gamma_{t-1}),
\end{align*}
where $J_t = U^{-1}A_t U$.
Now, since any Hurwitz matrix is similar to a PD matrix with an appropriate similarity transformation $U$, choosing $U$ this way we get that $\E[J_t]$ is PD, hence $P_U$ is PD.
\fi
%This completes the transformation of a Hurwitz problem $P$ to a positive definite problem $P_U$. 
The condition number $\cond{U}$ appears in our bound because $\theta_t$ is recovered from $\gamma_t$ using
$\theta_t=U\gamma_t$. Of course, when the problem $P$ is positive definite, we can let $U=\I$ in \Cref{th:rate}. 
More generally, one can always take $U$ in the result that leads to the smallest bound.

### 2017-05-19 intro.tex
up to conclusion

%!TEX root =  flsa.tex
\section{Introduction}
Linear stochastic approximation algorithms (LSAs) 
of the form
%We consider linear stochastic approximation algorithms (LSA) of the general form given by
\begin{align}\label{eq:lsaintro}
\theta_t=\theta_{t-1}+\alpha_t (b_t-A_t \theta_{t-1}),
\end{align}
with $(\alpha_t)_t$ a positive step-size sequence chosen by the user and 
$(b_t,A_t)\in \R^d\times \R^{\dcd}$,  $t\geq 0$, a sequence of identically distributed random variables is widely used in
machine learning, and in particular in reinforcement learning (RL), to compute the solution of the equation 
$\E[b_t] - \E[A_t] \theta = 0$, where $\E$ stands for mathematical expectation.
%where the iterates, $\theta_t\in \R^d$, and step-sizes, $\alpha_t>0$, are algorithmic quantities, and $(b_t,A_t), t\geq 0\in \R^d\times \R^{\dcd}$ is the noisy data sequence presented to the algorithm.
%LSAs are widely applied in machine learning and reinforcement learning (RL), where the aim is to compute an appropriate $\ts\in \R^d$ using only the noisy data sequence and $O(d)$ updates per iteration. 
Some examples of LSAs include the stochastic gradient descent algorithm (SGD) for the problem of linear regression with quadratic loss \cite{bach,bachaistats}, and the \emph{temporal difference} (TD) class of learning algorithms in RL \cite{sutton,konda-tsitsiklis,KoTsi03:LSA,gtd,gtd2,gtdmp}.
\todoc{konda-tsitsiklis reference resolved to tsitsiklis-van-roy. is this what you want?? I also added KoTsi03:LSA, maybe that's what you wanted.}
%An additional feature in these class of applications is that $A_t$ turns out to be a rank-$1$ matrix and $A_t\theta_{t-1}$ can be obtained in $O(d)$, which is attractive due to the cheap per time step computational requirement.\par

The choice of the step-size sequence $(\alpha_t)_t$ is critical for the performance of LSAs such as \eqref{eq:lsaintro}.
Informally speaking, smaller step-sizes are better for noise rejection and larger step-sizes lead to faster forgetting of initial conditions (smaller bias). At the same time, step-sizes that are too large might result in instability of \eqref{eq:lsaintro} even when $(A_t)_t$ has favourable properties. 
A useful choice has been the diminishing step-sizes \cite{gtd2,gtdmp,konda-tsitsiklis}, where $\alpha_t\ra 0$ such that $\sum_{t\geq 0} \alpha_t=\infty$. Here, $\alpha_t\to0$ circumvents the need for guessing the magnitude of step-sizes that stabilize the updates, while the second condition ensures that initial conditions are forgotten. 
An alternate idea, which we call LSA with constant step-size and Polyak-Ruppert averaging (LSA with CS-PR, in short), is to run \eqref{eq:lsaintro} by choosing $\alpha_t=\alpha>0$ $\forall t\geq 0$ with some $\alpha>0$, and output the average $\thh_t\eqdef\frac{1}{t+1}\sum_{i=0}^t \theta_i$. Thus, in LSA with CS-PR, $\theta_t$ is an internal variable and $\thh_t$ is the output of the algorithm. The idea is that the constant step-size leads to faster forgetting of initial conditions, while the averaging on the top
reduces noise.
This idea goes back to  \citet{ruppert} and \citet{polyak-judisky} who considered it in the context of stochastic approximation that LSA is a special case of. 
%Intuitively, the CS-PR technique can be seen to address the learning vs noise rejection trade-off, where the constant step-size takes care of the learning  and the averaging of the iterates takes care of the noise rejection.
\paragraph{Motivation and Contribution:} Recently, \citet{bach} considered stochastic gradient descent (SGD)\footnote{SGD is an LSA of the form in \eqref{eq:lsaintro}.} with CS-PR for the linear regression problem with quadratic loss and \iid sampling. They showed that one can calculate a constant step-size from only a bound on the magnitude of the noisy data so that the leading term as $t\to\infty$
\todoc{There is a subtlety here, because, if I believe you, 
\citet{bach} sells their result as a non-asymptotic result. How can they do this?
Can we be more explicit where in the paper $C_{P',\alpha}/t^2$ shows up -- see the notation below? We must be very explicit here.
The reviewers may not like this.
}
 in the mean-squared (regression) error after $t$ updates is at most $\frac{C}{t}$ with a constant $C>0$ that depends \emph{only} on the bound on the data, and is in particular independent of the eigenspectrum of $\E[A_t]$, a property which is not shared by other step-size tunings and variations of the basic SGD method.
\todoc{Dimension?}

@@

We also define a subclass  $\P_{\text{SPD},B}$ of problems, related to SGD for linear regression, that does `admit' a uniform constant step-size, thereby recovering a part of the result by \citet{bach}. \todoc{Why only part? We may need to explain the difference.} Our study thus sheds light on what structural assumptions are key to achieve a uniform bound for CS-PR.

>>>>

%!TEX root =  flsa.tex
\section{Introduction}\label{sec:intro}
Linear stochastic approximation algorithms (LSAs) 
of the form
%We consider linear stochastic approximation algorithms (LSA) of the general form given by
\begin{align}\label{eq:lsaintro}
\theta_t=\theta_{t-1}+\alpha_t (b_t-A_t \theta_{t-1}),
\end{align}
with $(\alpha_t)_t$ a positive step-size sequence chosen by the user and 
$(b_t,A_t)\in \R^d\times \R^{\dcd}$,  $t\geq 0$, a sequence of identically distributed random variables is widely used in
machine learning, and in particular in reinforcement learning (RL), to compute the solution of the equation 
$\E[b_t] - \E[A_t] \theta = 0$, where $\E$ stands for mathematical expectation.
%where the iterates, $\theta_t\in \R^d$, and step-sizes, $\alpha_t>0$, are algorithmic quantities, and $(b_t,A_t), t\geq 0\in \R^d\times \R^{\dcd}$ is the noisy data sequence presented to the algorithm.
%LSAs are widely applied in machine learning and reinforcement learning (RL), where the aim is to compute an appropriate $\ts\in \R^d$ using only the noisy data sequence and $O(d)$ updates per iteration. 
Some examples of LSAs include the stochastic gradient descent algorithm (SGD) for the problem of linear least-squares estimation  (LSE) \cite{bach,bachaistats}, and the \emph{temporal difference} (TD) class of learning algorithms in RL \cite{sutton,konda-tsitsiklis,KoTsi03:LSA,gtd,gtd2,gtdmp}.
\todoc{konda-tsitsiklis reference resolved to tsitsiklis-van-roy. is this what you want?? I also added KoTsi03:LSA, maybe that's what you wanted.}
%An additional feature in these class of applications is that $A_t$ turns out to be a rank-$1$ matrix and $A_t\theta_{t-1}$ can be obtained in $O(d)$, which is attractive due to the cheap per time step computational requirement.\par

The choice of the step-size sequence $(\alpha_t)_t$ is critical for the performance of LSAs such as \eqref{eq:lsaintro}.
Informally speaking, smaller step-sizes are better for noise rejection and larger step-sizes lead to faster forgetting of initial conditions (smaller bias). At the same time, step-sizes that are too large might result in instability of \eqref{eq:lsaintro} even when $(A_t)_t$ has favourable properties. 
A useful choice has been the diminishing step-sizes \cite{gtd2,gtdmp,konda-tsitsiklis}, where $\alpha_t\ra 0$ such that $\sum_{t\geq 0} \alpha_t=\infty$. Here, $\alpha_t\to0$ circumvents the need for guessing the magnitude of step-sizes that stabilize the updates, while the second condition ensures that initial conditions are forgotten. 
An alternate idea, which we call LSA with constant step-size and Polyak-Ruppert averaging (LSA with CS-PR, in short), is to run \eqref{eq:lsaintro} by choosing $\alpha_t=\alpha>0$ $\forall t\geq 0$ with some $\alpha>0$, and output the average $\thh_t\eqdef\frac{1}{t+1}\sum_{i=0}^t \theta_i$. Thus, in LSA with CS-PR, $\theta_t$ is an internal variable and $\thh_t$ is the output of the algorithm. The idea is that the constant step-size leads to faster forgetting of initial conditions, while the averaging on the top
reduces noise.
This idea goes back to  \citet{ruppert} and \citet{polyak-judisky} who considered it in the context of stochastic approximation that LSA is a special case of. 
%Intuitively, the CS-PR technique can be seen to address the learning vs noise rejection trade-off, where the constant step-size takes care of the learning  and the averaging of the iterates takes care of the noise rejection.
\paragraph{Motivation and Contribution:} Recently, \citet{bach} considered stochastic gradient descent (SGD)\footnote{SGD is an LSA of the form in \eqref{eq:lsaintro}.} with CS-PR for LSE and \iid sampling. They showed that one can calculate a constant step-size from only a bound on the magnitude of the noisy data so that the leading term as $t\to\infty$
 in the mean-squared prediction error after $t$ updates is at most $\frac{C}{t}$ with a constant $C>0$ that depends \emph{only} on the bound on the data, and is in particular independent of the eigenspectrum of $\E[A_t]$, a property which is not shared by other step-size tunings and variations of the basic SGD method.%
 \footnote{See \cref{sec:related} for further discussion of the nature of these results.}
\todoc{Dimension?}

@@

We also define a subclass  $\P_{\text{SPD},B}$ of problems, related to SGD for LSE, that does `admit' a uniform constant step-size, thereby recovering a part of the result by \citet{bach}.
Our results in particular shed light on the precise structural assumptions that are needed 
to achieve a uniform bound for CS-PR. 
For further details, see \cref{sec:related}.

### 2017-05-19 prob.tex
up to conclusion

In what follows, for $t\ge1$ we make use of the $\sigma$-fields $\F_{t-1}\eqdef\{\theta_0,A_1,\ldots, A_{t-1}, b_1,\ldots, b_{t-1}\}$; $\F_0$ holds all random variables. \todoc{A bit unusual as a choice.}
We are interested in the behaviour of \eqref{eq:lsa} under the following assumption:
\begin{assumption}\label{assmp:lsa}
\begin{enumerate}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item \label{dist} $(b_t, A_t)\sim P$, $t\geq 0$ is an \iid sequence.
We let $A_P$ be the expectation of $A_t$, $b_P$ be the expectation of $b_t$, as in \cref{def:dist}.
%where $P^b$ is a distribution over $\R^d$ and $P^A$ is a distribution over $\R^{\dcd}$. 
\todoc{I got rid off $P^b$ and $P^A$. There were $P^V$ and $P^M$ previously.. Confusing.}
We assume that $P$ is Hurwitz.
\item \label{matvar} The martingale difference sequences\footnote{$\EE{M_t|\F_{t-1}}=0$ and $\EE{N_t|\F_{t-1}}=0$} $M_t\eqdef A_t-A_{P}$ and $N_t\eqdef b_t-b_{P}$ associated with $A_t$ and $b_t$ satisfy the following \todoc{This would be the place to state if we make assumptions above the correlations between $M_t$ and $N_t$.}
\begin{align*}
	\E\left[ \norm{M_t}^2\mid\F_{t-1}\right]\leq \sigma^2_{A_P}\,, \qquad 
	\E[N_t^* N_t]=\sigma^2_{b_P}\,.
\end{align*}
with some $\sigma^2_{A_P}$ and $\sigma^2_{b_P}$. \todoc{Could not these just be $\sigma^2_A$, $\sigma^2_b$, or with $M$ and $V$?}
\item $A_P$ is invertible and thus the vector $\ts=A^{-1}_Pb_P$ is well-defined. \todoc{Bertsekas looked at the case when $\ts$ is well-defined but $A_P$ is not invertible. Future work..?}
\end{enumerate}
\end{assumption}
%For the rest of the paper we denote the errors of the internal and the output variables of \eqref{eq:lsa} at time $t$ by $e_t\eqdef \theta_t-\ts$ and $\eh_t\eqdef \thh_t-\ts$ respectively.
\paragraph{Performance Metric:}  
We are interested in the behavior of the mean squared error (MSE) at time $t$ given%
\footnote{More generally, one can be interested in $\EEP{\normsm{\thh_t-\ts}_C^2}$, the MSE with respect to a PD Hermitian matrix $C$. Since in general it is not possible to exploit the presence of $C$ unless it is connected to $P$ in a special way,
here we restrict ourselves to $C = \I$. For more discussion, including the discussion of the case of SGD for linear least-squares when $C$ and $P$ are favourably connected see \cref{sec:related}.}
 by $\EE{\normsm{\thh_t-\ts}^2}$. \todoc{Move up footnote. Polish..}
\begin{comment}
\footnote{We note here that $\E[\normsm{\thh_t-\ts}_C^2]$, which measures the MSE in the quadratic norm with respect to a positive definite matrix $C\succ 0$. However, unless $C$ has some special structure, it is not possible to exploit this generality in our bounds. Further, when data is bounded $\norm{C}^2$ is also bounded and it is straightforward to see that $\EEP{\norm{\thh_t-\ts}}^2_C\leq \norm{C}^2\EEP{\norm{\thh_t-\ts}^2}$. So, for the purpose of stating our results we will not use the general quadratic norm, however, will use it when we discuss the work by \cite{bach} in the linear regression setting, where its usage is relevant.}
\end{comment}
%We wish to understand how the MSE is affected by the choice of $\alpha$ and the spectral properties of $A_P$. Another aspect of interest is to understand the contribution of the \emph{bias} (caused by the initial condition $\theta_0$) and the \emph{variance} (caused by $\sigma^2_P,\sigma^2_b$) to the MSE.\par
\todoch{Mention importance of forgetting the bias etc. Mention that we really don't have control over $\norm{U}$}

>>>>

In what follows, for $t\ge1$ we make use of the $\sigma$-fields $\F_{t-1}\eqdef\{\theta_0,A_1,\ldots, A_{t-1}, b_1,\ldots, b_{t-1}\}$; $\F_{-1}$ is the trivial $\sigma$ algebra. \todoc{You wrote $\F_0$ holds all random variables, an unusual choice. And it does not work, I think and the index should be $-1$. The martingale property breaks otherwise with the first time step.}
We are interested in the behaviour of \eqref{eq:lsa} under the following assumption:
\begin{assumption}\label{assmp:lsa}
\begin{enumerate}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item \label{dist} $(b_t, A_t)\sim P$, $t\geq 0$ is an \iid sequence.
We let $A_P$ be the expectation of $A_t$, $b_P$ be the expectation of $b_t$, as in \cref{def:dist}.
%where $P^b$ is a distribution over $\R^d$ and $P^A$ is a distribution over $\R^{\dcd}$. 
\todoc{I got rid off $P^b$ and $P^A$. There were $P^V$ and $P^M$ previously.. Confusing.}
We assume that $P$ is Hurwitz.
\item \label{matvar} The martingale difference sequences\footnote{That is, $\EE{M_t|\F_{t-1}}=0$ and $\EE{N_t|\F_{t-1}}=0$ and $M_t,N_t$ are $\F_t$ measurable, $t\ge 0$.} $M_t\eqdef A_t-A_{P}$ and $N_t\eqdef b_t-b_{P}$ associated with $A_t$ and $b_t$ satisfy the following 
\todoc{So there is conditioning for $M_t$, and no conditions for $N_t$? Interesting. Maybe comment on this
that this is not a mistake.
Also, why write $N_t^* N_t$ instead of $\norm{N_t}^2$???}
\todoc{This would be the place to state if we make assumptions above the correlations between $M_t$ and $N_t$.}
\begin{align*}
	\E\left[ \norm{M_t}^2\mid\F_{t-1}\right]\leq \sigma^2_{A_P}\,, \qquad 
	\E[N_t^* N_t]=\sigma^2_{b_P}\,.
\end{align*}
with some $\sigma^2_{A_P}$ and $\sigma^2_{b_P}$. \todoc{Could not these just be $\sigma^2_A$, $\sigma^2_b$, or with $M$ and $V$?}
\item $A_P$ is invertible and thus the vector $\ts=A^{-1}_Pb_P$ is well-defined. \todoc{Bertsekas looked at the case when $\ts$ is well-defined but $A_P$ is not invertible. Future work..?}
\end{enumerate}
\end{assumption}
%For the rest of the paper we denote the errors of the internal and the output variables of \eqref{eq:lsa} at time $t$ by $e_t\eqdef \theta_t-\ts$ and $\eh_t\eqdef \thh_t-\ts$ respectively.
\paragraph{Performance Metric:}  
We are interested in the behavior of the mean squared error (MSE) at time $t$ given%
\footnote{More generally, one can be interested in $\EEP{\normsm{\thh_t-\ts}_C^2}$, the MSE with respect to a PD Hermitian matrix $C$. Since in general it is not possible to exploit the presence of $C$ unless it is connected to $P$ in a special way,
here we restrict ourselves to $C = \I$. For more discussion, including the discussion of the case of SGD for linear least-squares when $C$ and $P$ are favourably connected see \cref{sec:related}.}
 by $\EE{\normsm{\thh_t-\ts}^2}$. \todoc{Move up footnote. Polish..}
\begin{comment}
\footnote{We note here that $\E[\normsm{\thh_t-\ts}_C^2]$, which measures the MSE in the quadratic norm with respect to a positive definite matrix $C\succ 0$. However, unless $C$ has some special structure, it is not possible to exploit this generality in our bounds. Further, when data is bounded $\norm{C}^2$ is also bounded and it is straightforward to see that $\EEP{\norm{\thh_t-\ts}}^2_C\leq \norm{C}^2\EEP{\norm{\thh_t-\ts}^2}$. So, for the purpose of stating our results we will not use the general quadratic norm, however, will use it when we discuss the work by \cite{bach} in LSE, where its usage is relevant.}
\end{comment}
%We wish to understand how the MSE is affected by the choice of $\alpha$ and the spectral properties of $A_P$. Another aspect of interest is to understand the contribution of the \emph{bias} (caused by the initial condition $\theta_0$) and the \emph{variance} (caused by $\sigma^2_P,\sigma^2_b$) to the MSE.\par
\todoch{Mention importance of forgetting the bias etc. Mention that we really don't have control over $\norm{U}$}
